### 2018-09-27 ms.tex
Update cov table.

Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.

@@

Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
This has been accompanied by a strategic shift towards aiming for elimination in low burden countries \cite{world2016world, newby2016path}.
Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
We therefore need new data sources and associated statistical methods.

@@

Routine surveillance data, of disease case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
Surveillance data is commonly aggregated, reporting disease case counts that occurred within a certain geographic region defined by a polygon.
Ths surveillance data can be more sensitive than prevalence surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
Furthermore, surveillance data is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
However, the unstructured nature data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.

@@

Further to issues with the data itself, using aggregated data to estimate malaria risk for high resolution maps presents particular modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
The class of models that aim to estimate high-resolution maps from aggregated data are called disaggregation models and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
The aggregating of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
For example, Sturrock \emph{et al.} used only two environmental covariates in their model \cite{sturrock2014fine}.
Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software.
Wilson \emph{et al.} \cite{wilson2017pointless} use an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.

@@

Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihood functions for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for random crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Pearson & Indonesia & 0.28 & 0.46 &  0.42\\
&& Senegal & 0.28 & 0.79 &  0.83\\
&& Madagascar & 0.69 & 0.72 &  0.75\vspace{1mm}\\
& Spearman & Indonesia & 0.39 & 0.75 &  0.75\\
&& Senegal & 0.46 & 0.69 &  0.66\\
&& Madagascar & 0.81 & 0.83 &  0.85\vspace{3mm} \\
Prevalence & Pearson & Indonesia & 0.32 & 0.31 &  0.19\\
&& Senegal & 0.06 & 0.04 &  0.04\\
&& Madagascar & 0.57 & 0.55 &  0.59\vspace{1mm}\\
& Spearman & Indonesia & 0.54 & 0.38 &  0.39\\
&& Senegal & 0.03 & 0.12 &  0.12\\
&& Madagascar & 0.57 & 0.55 &  0.58\\
\end{tabular}
\begin{flushleft}
Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for spatial crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Metric} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Pearson & Indonesia &  0.07 &  0.09 &   0.16\\
&& Senegal &  0.20 &  0.23 &   0.53\\
&& Madagascar &  0.20 &  0.16 &   0.24\vspace{1mm}\\
& Spearman & Indonesia &  0.40 &  0.47 &   0.39\\
&& Senegal &  0.36 &  0.30 &   0.56\\
&& Madagascar &  0.49 &  0.50 &   0.52\vspace{3mm} \\
Prevalence & Pearson & Indonesia & -0.23 & -0.07 &   0.06\\
&& Senegal &  0.16 &  0.19 &   0.16\\
&& Madagascar &  0.23 &  0.17 &   0.21\vspace{1mm}\\
& Spearman & Indonesia & -0.35 & -0.05 &  -0.01\\
&& Senegal &  0.02 &  0.16 &   0.13\\
&& Madagascar &  0.44 &  0.38 &   0.43\\
\end{tabular}
\begin{flushleft}
Correlation (Spearman's and Pearson's) of predicted incidence rate and prevalence against out-of-sample observed data for three countries.
The data were split spatiall into 5 groups.
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) log10 aggregated incidence, B, D, F) prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{predobsscatter}
\end{figure}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.10 & 0.76 &  0.77\\
&& Senegal & 0.69 & 0.82 &  0.78\\
&& Madagascar & 0.73 & 0.82 &  0.78\vspace{1mm}\\
& Spatial & Indonesia & 0.10 & 0.76 &  0.77\\
&& Senegal & 0.69 & 0.82 &  0.78\\
&& Madagascar & 0.73 & 0.82 &  0.78\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.83 & 0.59 &  0.77\\
&& Senegal & 0.87 & 0.69 &  0.80\\
&& Madagascar & 0.83 & 0.69 &  0.80\vspace{1mm}\\
& Spatial & Indonesia & 0.54 & 0.36 &  0.38\\
&& Senegal & 0.87 & 0.69 &  0.80\\
&& Madagascar & 0.83 & 0.69 &  0.80\\
\end{tabular}
\begin{flushleft}

>>>>

@@

Global malaria incidence has decreased dramatically over the last 20 years \cite{abajobir2017global, bhatt2015effect}.
This decrease has been accompanied by a strategic shift towards aiming for elimination in low incidence countries \cite{world2016world, newby2016path}.
Accurate, high-resolution maps of malaria risk are vital in countries in the elimination and pre-elimination phases \cite{sturrock2016mapping, cohen2017mapping}.
However, mapping malaria in low burden countries presents new challenges as traditional mapping of prevalence \cite{gething2011new, bhatt2017improved, gething2012long} using cluster-level surveys and model-based geostatistics are not necessarily effective in these areas \cite {sturrock2016mapping, sturrock2014fine}.
In low burden areas, very large sample sizes are needed before a prevalence survey is informative.
Furthermore, large, countrywide surveys of prevalence, such as DHS or MIS, are rare in low burden countries due to costs and percieved low utility \cite{dhs}.
We therefore need new data sources and associated statistical methods.

%Despite major reductions in incidence over the last fifteen years, malaria still causes millions of deaths and loads of DALYs annually \cite{abajobir2017global}.
%Elimination of malaria, country-by-county has become a central goal in the global malaria strategy \cite{world2016world}.
%Elimination of malaria requires high resolution maps of malaria risk, in low prevalence areas in order to optimise interventions and minimise costs \cite{sturrock2016mapping}.

@@

Routine surveillance data, of malaria case counts, is becoming more widely available and of better quality \cite{sturrock2016mapping, ohrt2015information, cibulskis2011worldwide}.
Surveillance data is commonly aggregated, reporting the number of cases that occurred within a certain geographic or administrative region defined by a polygon.
Ths surveillance data can be more sensitive than prevalence surveys in low transmission areas as the entire public health system is being used to passively monitor disease risk \cite{cibulskis2011worldwide}.
Furthermore, surveillance data is also often timely, with reports being released annually or monthly, while large prevalence surveys are performed on a more decadely time scale.
However, the unstructured nature of data collection and reporting from national disease surveillance systems means that dealing with biases and data gaps is an ongoing research priority \cite{battle2016treatment, cibulskis2011worldwide}.

@@

Further to issues with the data itself, using aggregated data to estimate malaria risk for high resolution maps presents particular modelling difficulties \cite{sturrock2014fine, wilson2017pointless, law2018variational, taylor2017continuous, li2012log}.
%Disaggregation models aim to estimate high-resolution maps from aggregated data and are characterised by having a variable number of pixels, and therefore multiple rows of covariate data, per row of response data.
The aggregating of cases over space means that the data may be relatively uninformative, especially if the case counts are aggregated over a large or heterogenous area.
For example, Sturrock \emph{et al.} used only two environmental covariates in their model \cite{sturrock2014fine}.
Disaggregation models are also simply an underrepresented class of models in the statistical literature and statistical software.
Wilson \emph{et al.} \cite{wilson2017pointless} used an approximation to represent a downscaling model as a convolution matrix within R-INLA \cite{INLA} but more generally, downscaling models are not available in popular software packages and must be programmed explicitely.
Furthermore, disaggregation models are relatively difficult to implement as they have more rows of covariate data than response data.

@@

Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihoods for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for random crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia & 18.33 & 14.02 &  14.09\\
& Senegal & 51.24 & 26.74 &  28.45\\
& Madagascar & 85.54 & 37.45 &  34.49\vspace{3mm}\\
Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
& Senegal & 0.015 & 0.024 &  0.024\\
& Madagascar & 0.054 & 0.059 &  0.059\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for spatial crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia &  18.13 &  14.77 &   15.02\\
& Senegal &  51.17 &  41.43 &   36.76\\
& Madagascar & 107.32 &  71.44 &   65.50\vspace{3mm}\\
Prevalence & Indonesia & 0.011 & 0.010 &  0.010\\
& Senegal & 0.015 & 0.019 &  0.019\\
& Madagascar & 0.069 & 0.066 &  0.065\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split spatiall into 5 groups.
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{predobsscatter}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{predobsscatter}
\end{figure}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
&& Senegal & 0.11 & 0.80 &  0.85\\
&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
&& Senegal & 0.30 & 0.67 &  0.70\\
&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
&& Senegal & 0.80 & 0.71 &  0.91\\
&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
&& Senegal & 0.90 & 0.88 &  0.79\\
&& Madagascar & 0.93 & 0.68 &  0.83\\
\end{tabular}
\begin{flushleft}
